---
title: Data and Analyes for 'Bad bankers no more? Truth-telling and (dis)honesty in
  the finance industry'
author: "Christoph Huber, Juergen Huber"
output:
  html_notebook:
    df_print: tibble
    fig_caption: yes
    fig_height: 6
    fig_width: 8
    theme: lumen
    toc: yes
    toc_depth: 2
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


 

# Intro

This file contains R-code to replicate all analyses, tables, and figures in '_Bad bankers no more? Truth-telling and (dis)honesty in the finance industry_'.

The experiments were run between November 2018 and January 2020 with oTree by Chen et al. (2016).
All analyses were conducted in R.

Required R-packages:

```{r message=FALSE, warning=FALSE}
library(plyr)
library(tidyverse)
library(readxl)
library(wesanderson)
library(ggthemes)
library(kableExtra)
library(stargazer)
library(lfe)
library(viridis)
library(car)
library(Rmisc)
```

First, we import, tidy, reshape, and merge the raw data files from the experiment (see below).  
__To skip this step__, load the following `.RData`-files and go to section _Analysis_:

```{r}
load("_norms_before.RData")
load("_norms_stud.RData")
load("_norms_studprof.RData")
load("_tt_before.RData")
load("_tt_pf.RData")
load("_tt_stud.RData")
load("_tt.RData")
load("_norms.RData")
load("_reshaped.RData")
load("_reshaped_norms.RData")
load("_merge.RData")
```


# Data preparation 

## Import and tidy data

The following commands import the raw experiment output from folder `_raw` as an `.xlsx`-file into R, converts it into a tibble, and tidies and organises all relevant variables.  

### Import and tidy data from STUD

```{R}
csv <- read_xlsx("_raw/data_students1/all_apps_wide_2018-12-14.xlsx") 
csv1 <- read.csv("_raw/data_students2fin/all_apps_wide_2020-01-17.csv")
csv2 <- read.csv("_raw/data_students2neu/all_apps_wide_2020-01-17.csv")
csv3 <- read.csv("_raw/data_students2abs/all_apps_wide_2020-01-17.csv")

data <- tbl_df(csv)
data <- data %>% rbind.fill(csv1, csv2, csv3)

tt_stud <- data %>%
  filter((session.code == "6vi3dw2b"|session.code == "9auk5aea"|session.code=="7q355nra"|session.code == "s1pa9lws"|session.code == "9d565pyp"|session.code == "o75chhp9"), participant._index_in_pages>=11)

tt_stud <- tt_stud %>%
  rename(session = session.code,
         context = tt.1.player.context,
         treatment = tt.1.player.treatment,
         subject = participant.code,
         choice1 = tt.1.player.choice_1,
         choice2 = tt.1.player.choice_2,
         choice3 = tt.1.player.choice_3,
         choice4 = tt.1.player.choice_4,
         choice5 = tt.1.player.choice_5,
         belief1 = tt.1.player.belief_1,
         belief2 = tt.1.player.belief_2,
         belief3 = tt.1.player.belief_3,
         belief4 = tt.1.player.belief_4,
         belief5 = tt.1.player.belief_5,
         order = tt.1.player.order,
         severity = tt.1.player.severity,
         reputation = tt.1.player.reputation,         
         pref1_1 = postexp.1.player.pref1_1,
         pref1_2 = postexp.1.player.pref1_2,
         pref1_3 = postexp.1.player.pref1_3,
         pref1_4 = postexp.1.player.pref1_4,
         pref2_1 = postexp.1.player.pref2_1,
         pref2_2 = postexp.1.player.pref2_2,
         pref2_3 = postexp.1.player.pref2_3,         
         risk = postexp.1.player.risk_aversion1,
         age = postexp.1.player.age,
         female = postexp.1.player.female,
         education = postexp.1.player.education,
         job = postexp.1.player.jobfunction,
         investment = postexp.1.player.investment,
         whichinvestment = postexp.1.player.whichinvestment,
         payoff = participant.payoff) %>%
  mutate(tt = 1,
         word1 = paste0(wordscra.1.player.word1_1,
                        wordscra.1.player.word1_2,
                        wordscra.1.player.word1_3,
                        wordscra.1.player.word1_4,
                        wordscra.1.player.word1_5),
         word2 = paste0(wordscra.1.player.word2_1,
                        wordscra.1.player.word2_2,
                        wordscra.1.player.word2_3),
         word3 = paste0(wordscra.1.player.word3_1,
                        wordscra.1.player.word3_2,
                        wordscra.1.player.word3_3,
                        wordscra.1.player.word3_4,
                        wordscra.1.player.word3_5,
                        wordscra.1.player.word3_6),
         word4 = paste0(wordscra.1.player.word4_1,
                        wordscra.1.player.word4_2,
                        wordscra.1.player.word4_3,
                        wordscra.1.player.word4_4,
                        wordscra.1.player.word4_5),
         word5 = paste0(wordscra.1.player.word5_1,
                        wordscra.1.player.word5_2,
                        wordscra.1.player.word5_3,
                        wordscra.1.player.word5_4,
                        wordscra.1.player.word5_5),
         word6 = paste0(wordscra.1.player.word6_1,
                        wordscra.1.player.word6_2,
                        wordscra.1.player.word6_3,
                        wordscra.1.player.word6_4),
         word1f = ifelse(word1 == tools::toTitleCase(tolower("stock")), 1, 0),
         word3f = ifelse(word3 == tools::toTitleCase(tolower("broker")), 1, 0),
         word4f = ifelse(word4 == tools::toTitleCase(tolower("money")), 1, 0),
         word6f = ifelse(word6 == tools::toTitleCase(tolower("bond")), 1, 0),
         wordsf = word1f + word3f + word4f + word6f,
         lies = choice1 + choice2 + choice3 + choice4 + choice5,
         beliefs = belief1/100 + belief2/100 + belief3/100 + belief4/100 + belief5/100
         ) %>%  
  select(-starts_with("participant."),
         -starts_with("session."),
         -starts_with("postexp"),
         -starts_with("tt."),
         -starts_with("tt_norms."),
         -starts_with("bt."),
         -starts_with("wordscra.")) %>%
  arrange(session, context, subject) %>%
  group_by(context)

norms_stud <- data %>%
  filter((session.code == "f7hlbgua"|session.code == "r8k3mqov"|session.code=="23zy7355")
         & participant._index_in_pages==27)

norms_stud <- norms_stud %>%
  rename(session = session.code,
         context = tt_norms.1.player.context,
         subject = participant.code,
         norms_true1 = tt_norms.1.player.norm_true,
         norms_true2 = tt_norms.2.player.norm_true,
         norms_true3 = tt_norms.3.player.norm_true,
         norms_true4 = tt_norms.4.player.norm_true,
         norms_true5 = tt_norms.5.player.norm_true,
         norms_false1 = tt_norms.1.player.norm_false,
         norms_false2 = tt_norms.2.player.norm_false,
         norms_false3 = tt_norms.3.player.norm_false,
         norms_false4 = tt_norms.4.player.norm_false,
         norms_false5 = tt_norms.5.player.norm_false,
         belief1 = tt_norms.5.player.belief_1,
         belief2 = tt_norms.5.player.belief_2,
         belief3 = tt_norms.5.player.belief_3,
         belief4 = tt_norms.5.player.belief_4,
         belief5 = tt_norms.5.player.belief_5,
         order = tt_norms.1.player.order,
         pref1_1 = postexp.1.player.pref1_1,
         pref1_2 = postexp.1.player.pref1_2,
         pref1_3 = postexp.1.player.pref1_3,
         pref1_4 = postexp.1.player.pref1_4,
         pref2_1 = postexp.1.player.pref2_1,
         pref2_2 = postexp.1.player.pref2_2,
         pref2_3 = postexp.1.player.pref2_3,         
         risk = postexp.1.player.risk_aversion1,
         age = postexp.1.player.age,
         female = postexp.1.player.female,
         education = postexp.1.player.education,
         job = postexp.1.player.jobfunction,
         investment = postexp.1.player.investment,
         whichinvestment = postexp.1.player.whichinvestment) %>%
  mutate(tt = 0,
         word1 = paste0(wordscra.1.player.word1_1,
                        wordscra.1.player.word1_2,
                        wordscra.1.player.word1_3,
                        wordscra.1.player.word1_4,
                        wordscra.1.player.word1_5),
         word2 = paste0(wordscra.1.player.word2_1,
                        wordscra.1.player.word2_2,
                        wordscra.1.player.word2_3),
         word3 = paste0(wordscra.1.player.word3_1,
                        wordscra.1.player.word3_2,
                        wordscra.1.player.word3_3,
                        wordscra.1.player.word3_4,
                        wordscra.1.player.word3_5,
                        wordscra.1.player.word3_6),
         word4 = paste0(wordscra.1.player.word4_1,
                        wordscra.1.player.word4_2,
                        wordscra.1.player.word4_3,
                        wordscra.1.player.word4_4,
                        wordscra.1.player.word4_5),
         word5 = paste0(wordscra.1.player.word5_1,
                        wordscra.1.player.word5_2,
                        wordscra.1.player.word5_3,
                        wordscra.1.player.word5_4,
                        wordscra.1.player.word5_5),
         word6 = paste0(wordscra.1.player.word6_1,
                        wordscra.1.player.word6_2,
                        wordscra.1.player.word6_3,
                        wordscra.1.player.word6_4),
         word1f = ifelse(word1 == tools::toTitleCase(tolower("stock")), 1, 0),
         word3f = ifelse(word3 == tools::toTitleCase(tolower("broker")), 1, 0),
         word4f = ifelse(word4 == tools::toTitleCase(tolower("money")), 1, 0),
         word6f = ifelse(word6 == tools::toTitleCase(tolower("bond")), 1, 0),
         wordsf = word1f + word3f + word4f + word6f,       
         beliefs = belief1/100 + belief2/100 + belief3/100 + belief4/100 + belief5/100
         ) %>%
  select(-starts_with("participant."),
         -starts_with("session."),
         -starts_with("postexp"),
         -starts_with("tt_norms."),
         -starts_with("tt."),
         -starts_with("bt."),
         -starts_with("wordscra.")) %>%
  arrange(session, context, subject) %>%
  group_by(context)

norms_stud <- norms_stud %>%
  mutate(norms_false1 = (norms_false1-3.5) / 2.5,
         norms_false2 = (norms_false2-3.5) / 2.5,
         norms_false3 = (norms_false3-3.5) / 2.5,
         norms_false4 = (norms_false4-3.5) / 2.5,
         norms_false5 = (norms_false5-3.5) / 2.5,
         norms_true1 = (norms_true1-3.5) / 2.5,
         norms_true2 = (norms_true2-3.5) / 2.5,
         norms_true3 = (norms_true3-3.5) / 2.5,
         norms_true4 = (norms_true4-3.5) / 2.5,
         norms_true5 = (norms_true5-3.5) / 2.5,
         norms_false = (norms_false1 + norms_false2 + norms_false3 + norms_false4)/4,
         norms_true = (norms_true1 + norms_true2 + norms_true3 + norms_true4)/4)

save(tt_stud, file="_tt_stud.RData")
save(norms_stud, file="_norms_stud.RData")
```


### Import and tidy data from PROF (before.world)

```{R}
csv <- read.csv("_raw/data_before/all_apps_wide_2019-02-27.csv")
data <- tbl_df(csv)

tt_before <- data %>%
  filter((session.code == "sl4o33w2") 
         & participant._index_in_pages==12)

tt_before <- tt_before %>%
  rename(session = session.code,
         context = tt.1.player.context,
         subject = participant.code,
         choice1 = tt.1.player.choice_1,
         choice2 = tt.1.player.choice_2,
         choice3 = tt.1.player.choice_3,
         choice4 = tt.1.player.choice_4,
         choice5 = tt.1.player.choice_5,
         belief1 = tt.1.player.belief_1,
         belief2 = tt.1.player.belief_2,
         belief3 = tt.1.player.belief_3,
         belief4 = tt.1.player.belief_4,
         belief5 = tt.1.player.belief_5,
         order = tt.1.player.order,
         pref1_1 = postexp.1.player.pref1_1,
         pref1_2 = postexp.1.player.pref1_2,
         pref1_3 = postexp.1.player.pref1_3,
         pref1_4 = postexp.1.player.pref1_4,
         pref2_1 = postexp.1.player.pref2_1,
         pref2_2 = postexp.1.player.pref2_2,
         pref2_3 = postexp.1.player.pref2_3,
         risk = postexp.1.player.risk_aversion1,
         age = postexp.1.player.age,
         female = postexp.1.player.female,
         education = postexp.1.player.education,
         job = postexp.1.player.jobfunction,
         investment = postexp.1.player.investment,
         whichinvestment = postexp.1.player.whichinvestment,
         finnews = postexp.1.player.finnews,
         payoff = participant.payoff) %>%
  mutate(tt = 1,
         word1 = paste0(wordscra.1.player.word1_1,
                        wordscra.1.player.word1_2,
                        wordscra.1.player.word1_3,
                        wordscra.1.player.word1_4,
                        wordscra.1.player.word1_5),
         word2 = paste0(wordscra.1.player.word2_1,
                        wordscra.1.player.word2_2,
                        wordscra.1.player.word2_3),
         word3 = paste0(wordscra.1.player.word3_1,
                        wordscra.1.player.word3_2,
                        wordscra.1.player.word3_3,
                        wordscra.1.player.word3_4,
                        wordscra.1.player.word3_5,
                        wordscra.1.player.word3_6),
         word4 = paste0(wordscra.1.player.word4_1,
                        wordscra.1.player.word4_2,
                        wordscra.1.player.word4_3,
                        wordscra.1.player.word4_4,
                        wordscra.1.player.word4_5),
         word5 = paste0(wordscra.1.player.word5_1,
                        wordscra.1.player.word5_2,
                        wordscra.1.player.word5_3,
                        wordscra.1.player.word5_4,
                        wordscra.1.player.word5_5),
         word6 = paste0(wordscra.1.player.word6_1,
                        wordscra.1.player.word6_2,
                        wordscra.1.player.word6_3,
                        wordscra.1.player.word6_4),
         word1f = ifelse(word1 == tools::toTitleCase(tolower("stock")), 1, 0),
         word3f = ifelse(word3 == tools::toTitleCase(tolower("broker")), 1, 0),
         word4f = ifelse(word4 == tools::toTitleCase(tolower("money")), 1, 0),
         word6f = ifelse(word6 == tools::toTitleCase(tolower("bond")), 1, 0),
         wordsf = word1f + word3f + word4f + word6f,
         lies = choice1 + choice2 + choice3 + choice4 + choice5,
         beliefs = belief1/100 + belief2/100 + belief3/100 + belief4/100 + belief5/100
  ) %>%  
  select(-starts_with("participant."),
         -starts_with("session."),
         -starts_with("postexp"),
         -starts_with("tt."),
         -starts_with("tt_norms."),
         -starts_with("bt."),
         -starts_with("wordscra."),
         -starts_with("redirect.")) %>%
  arrange(session, context, subject) %>%
  group_by(context)

norms_before <- data %>%
  filter((session.code == "jzmo442c")
         & participant._index_in_pages==28)

norms_before <- norms_before %>%
  rename(session = session.code,
         context = tt_norms.1.player.context,
         subject = participant.code,
         norms_true1 = tt_norms.1.player.norm_true,
         norms_true2 = tt_norms.2.player.norm_true,
         norms_true3 = tt_norms.3.player.norm_true,
         norms_true4 = tt_norms.4.player.norm_true,
         norms_true5 = tt_norms.5.player.norm_true,
         norms_false1 = tt_norms.1.player.norm_false,
         norms_false2 = tt_norms.2.player.norm_false,
         norms_false3 = tt_norms.3.player.norm_false,
         norms_false4 = tt_norms.4.player.norm_false,
         norms_false5 = tt_norms.5.player.norm_false,
         belief1 = tt_norms.5.player.belief_1,
         belief2 = tt_norms.5.player.belief_2,
         belief3 = tt_norms.5.player.belief_3,
         belief4 = tt_norms.5.player.belief_4,
         belief5 = tt_norms.5.player.belief_5,
         order = tt_norms.1.player.order,
         pref1_1 = postexp.1.player.pref1_1,
         pref1_2 = postexp.1.player.pref1_2,
         pref1_3 = postexp.1.player.pref1_3,
         pref1_4 = postexp.1.player.pref1_4,
         pref2_1 = postexp.1.player.pref2_1,
         pref2_2 = postexp.1.player.pref2_2,
         pref2_3 = postexp.1.player.pref2_3,         
         risk = postexp.1.player.risk_aversion1,
         age = postexp.1.player.age,
         female = postexp.1.player.female,
         education = postexp.1.player.education,
         job = postexp.1.player.jobfunction,
         investment = postexp.1.player.investment,
         whichinvestment = postexp.1.player.whichinvestment,
         finnews = postexp.1.player.finnews) %>%
  mutate(tt = 0,
         word1 = paste0(wordscra.1.player.word1_1,
                        wordscra.1.player.word1_2,
                        wordscra.1.player.word1_3,
                        wordscra.1.player.word1_4,
                        wordscra.1.player.word1_5),
         word2 = paste0(wordscra.1.player.word2_1,
                        wordscra.1.player.word2_2,
                        wordscra.1.player.word2_3),
         word3 = paste0(wordscra.1.player.word3_1,
                        wordscra.1.player.word3_2,
                        wordscra.1.player.word3_3,
                        wordscra.1.player.word3_4,
                        wordscra.1.player.word3_5,
                        wordscra.1.player.word3_6),
         word4 = paste0(wordscra.1.player.word4_1,
                        wordscra.1.player.word4_2,
                        wordscra.1.player.word4_3,
                        wordscra.1.player.word4_4,
                        wordscra.1.player.word4_5),
         word5 = paste0(wordscra.1.player.word5_1,
                        wordscra.1.player.word5_2,
                        wordscra.1.player.word5_3,
                        wordscra.1.player.word5_4,
                        wordscra.1.player.word5_5),
         word6 = paste0(wordscra.1.player.word6_1,
                        wordscra.1.player.word6_2,
                        wordscra.1.player.word6_3,
                        wordscra.1.player.word6_4),
         word1f = ifelse(word1 == tools::toTitleCase(tolower("stock")), 1, 0),
         word3f = ifelse(word3 == tools::toTitleCase(tolower("broker")), 1, 0),
         word4f = ifelse(word4 == tools::toTitleCase(tolower("money")), 1, 0),
         word6f = ifelse(word6 == tools::toTitleCase(tolower("bond")), 1, 0),
         wordsf = word1f + word3f + word4f + word6f,       
         beliefs = belief1/100 + belief2/100 + belief3/100 + belief4/100 + belief5/100
  ) %>%
  select(-starts_with("participant."),
         -starts_with("session."),
         -starts_with("postexp"),
         -starts_with("tt_norms."),
         -starts_with("tt."),
         -starts_with("bt."),
         -starts_with("wordscra."),
         -starts_with("redirect.")) %>%
  arrange(session, context, subject) %>%
  group_by(context)

norms_before <- norms_before %>%
  mutate(norms_false1 = (norms_false1-3.5) / 2.5,
         norms_false2 = (norms_false2-3.5) / 2.5,
         norms_false3 = (norms_false3-3.5) / 2.5,
         norms_false4 = (norms_false4-3.5) / 2.5,
         norms_false5 = (norms_false5-3.5) / 2.5,
         norms_true1 = (norms_true1-3.5) / 2.5,
         norms_true2 = (norms_true2-3.5) / 2.5,
         norms_true3 = (norms_true3-3.5) / 2.5,
         norms_true4 = (norms_true4-3.5) / 2.5,
         norms_true5 = (norms_true5-3.5) / 2.5,
         norms_false = (norms_false1 + norms_false2 + norms_false3 + norms_false4)/4,
         norms_true = (norms_true1 + norms_true2 + norms_true3 + norms_true4)/4)

save(tt_before, file="_tt_before.RData")
save(norms_before, file="_norms_before.RData")
```


### Import and tidy data from STUDPROF.

```{R}
csv <- read_xlsx("_raw/data_studprof/all_apps_wide_2019-04-15.xlsx") 

data <- tbl_df(csv)

norms_studprof <- data %>%
  filter((session.code == "7v1jo4vk")
         & participant._index_in_pages==27)

norms_studprof <- norms_studprof %>%
  rename(session = session.code,
         context = tt_norms.1.player.context,
         subject = participant.code,
         norms_true1 = tt_norms.1.player.norm_true,
         norms_true2 = tt_norms.2.player.norm_true,
         norms_true3 = tt_norms.3.player.norm_true,
         norms_true4 = tt_norms.4.player.norm_true,
         norms_true5 = tt_norms.5.player.norm_true,
         norms_false1 = tt_norms.1.player.norm_false,
         norms_false2 = tt_norms.2.player.norm_false,
         norms_false3 = tt_norms.3.player.norm_false,
         norms_false4 = tt_norms.4.player.norm_false,
         norms_false5 = tt_norms.5.player.norm_false,
         belief1 = tt_norms.5.player.belief_1,
         belief2 = tt_norms.5.player.belief_2,
         belief3 = tt_norms.5.player.belief_3,
         belief4 = tt_norms.5.player.belief_4,
         belief5 = tt_norms.5.player.belief_5,
         order = tt_norms.1.player.order,
         pref1_1 = postexp.1.player.pref1_1,
         pref1_2 = postexp.1.player.pref1_2,
         pref1_3 = postexp.1.player.pref1_3,
         pref1_4 = postexp.1.player.pref1_4,
         pref2_1 = postexp.1.player.pref2_1,
         pref2_2 = postexp.1.player.pref2_2,
         pref2_3 = postexp.1.player.pref2_3,         
         risk = postexp.1.player.risk_aversion1,
         age = postexp.1.player.age,
         female = postexp.1.player.female,
         education = postexp.1.player.education,
         job = postexp.1.player.jobfunction,
         investment = postexp.1.player.investment,
         whichinvestment = postexp.1.player.whichinvestment) %>%
  mutate(tt = 0,
         word1 = paste0(wordscra.1.player.word1_1,
                        wordscra.1.player.word1_2,
                        wordscra.1.player.word1_3,
                        wordscra.1.player.word1_4,
                        wordscra.1.player.word1_5),
         word2 = paste0(wordscra.1.player.word2_1,
                        wordscra.1.player.word2_2,
                        wordscra.1.player.word2_3),
         word3 = paste0(wordscra.1.player.word3_1,
                        wordscra.1.player.word3_2,
                        wordscra.1.player.word3_3,
                        wordscra.1.player.word3_4,
                        wordscra.1.player.word3_5,
                        wordscra.1.player.word3_6),
         word4 = paste0(wordscra.1.player.word4_1,
                        wordscra.1.player.word4_2,
                        wordscra.1.player.word4_3,
                        wordscra.1.player.word4_4,
                        wordscra.1.player.word4_5),
         word5 = paste0(wordscra.1.player.word5_1,
                        wordscra.1.player.word5_2,
                        wordscra.1.player.word5_3,
                        wordscra.1.player.word5_4,
                        wordscra.1.player.word5_5),
         word6 = paste0(wordscra.1.player.word6_1,
                        wordscra.1.player.word6_2,
                        wordscra.1.player.word6_3,
                        wordscra.1.player.word6_4),
         word1f = ifelse(word1 == tools::toTitleCase(tolower("stock")), 1, 0),
         word3f = ifelse(word3 == tools::toTitleCase(tolower("broker")), 1, 0),
         word4f = ifelse(word4 == tools::toTitleCase(tolower("money")), 1, 0),
         word6f = ifelse(word6 == tools::toTitleCase(tolower("bond")), 1, 0),
         wordsf = word1f + word3f + word4f + word6f,       
         beliefs = belief1/100 + belief2/100 + belief3/100 + belief4/100 + belief5/100
         ) %>%
  select(-starts_with("participant."),
         -starts_with("session."),
         -starts_with("postexp"),
         -starts_with("tt_norms."),
         -starts_with("tt."),
         -starts_with("bt."),
         -starts_with("wordscra.")) %>%
  arrange(session, context, subject) %>%
  group_by(context)

norms_studprof <- norms_studprof %>%
  mutate(norms_false1 = (norms_false1-3.5) / 2.5,
         norms_false2 = (norms_false2-3.5) / 2.5,
         norms_false3 = (norms_false3-3.5) / 2.5,
         norms_false4 = (norms_false4-3.5) / 2.5,
         norms_false5 = (norms_false5-3.5) / 2.5,
         norms_true1 = (norms_true1-3.5) / 2.5,
         norms_true2 = (norms_true2-3.5) / 2.5,
         norms_true3 = (norms_true3-3.5) / 2.5,
         norms_true4 = (norms_true4-3.5) / 2.5,
         norms_true5 = (norms_true5-3.5) / 2.5,
         norms_false = (norms_false1 + norms_false2 + norms_false3 + norms_false4)/4,
         norms_true = (norms_true1 + norms_true2 + norms_true3 + norms_true4)/4)

save(norms_studprof, file="_norms_studprof.RData")
```


### Import and tidy data from PROLIFIC

```{R}
csv <- read.csv("_raw/data_prolific/all_apps_wide_2020-01-08.csv")
csv1 <- read.csv("_raw/data_prolific/all_apps_wide_2020-01-14.csv")
csv2 <- read.csv("_raw/data_prolific/all_apps_wide_2020-01-17.csv")

data <- rbind(csv, csv1, csv2) %>% tbl_df()

exp <- read.csv("_raw/data_prolific/prolific_export_5e1478086e8aaba68ddcfa31.csv") %>% 
  rename(participant.label = participant_id,
         age.prolific = age)

data <- left_join(data, exp,
                  by=c("participant.label"))

tt_pf <- data %>%
  filter((session.code == "cfs9uxep"|session.code == "t3qqecpo"|session.code == "b7rrvg7s") 
         & participant._index_in_pages==12)

tt_pf <- tt_pf %>%
  rename(session = session.code,
         context = tt.1.player.context,
         treatment = tt.1.player.treatment,
         subject = participant.code,
         choice1 = tt.1.player.choice_1,
         choice2 = tt.1.player.choice_2,
         choice3 = tt.1.player.choice_3,
         choice4 = tt.1.player.choice_4,
         choice5 = tt.1.player.choice_5,
         belief1 = tt.1.player.belief_1,
         belief2 = tt.1.player.belief_2,
         belief3 = tt.1.player.belief_3,
         belief4 = tt.1.player.belief_4,
         belief5 = tt.1.player.belief_5,
         order = tt.1.player.order,
         severity = tt.1.player.severity,
         reputation = tt.1.player.reputation,
         pref1_1 = postexp.1.player.pref1_1,
         pref1_2 = postexp.1.player.pref1_2,
         pref1_3 = postexp.1.player.pref1_3,
         pref1_4 = postexp.1.player.pref1_4,
         pref2_1 = postexp.1.player.pref2_1,
         pref2_2 = postexp.1.player.pref2_2,
         pref2_3 = postexp.1.player.pref2_3,
         risk = postexp.1.player.risk_aversion1,
         age = postexp.1.player.age,
         female = postexp.1.player.female,
         education = postexp.1.player.education,
         job = postexp.1.player.jobfunction,
         investment = postexp.1.player.investment,
         whichinvestment = postexp.1.player.whichinvestment,
         finnews = postexp.1.player.finnews,
         payoff = participant.payoff) %>%
  mutate(tt = 1,
         word1 = paste0(wordscra.1.player.word1_1,
                        wordscra.1.player.word1_2,
                        wordscra.1.player.word1_3,
                        wordscra.1.player.word1_4,
                        wordscra.1.player.word1_5),
         word2 = paste0(wordscra.1.player.word2_1,
                        wordscra.1.player.word2_2,
                        wordscra.1.player.word2_3),
         word3 = paste0(wordscra.1.player.word3_1,
                        wordscra.1.player.word3_2,
                        wordscra.1.player.word3_3,
                        wordscra.1.player.word3_4,
                        wordscra.1.player.word3_5,
                        wordscra.1.player.word3_6),
         word4 = paste0(wordscra.1.player.word4_1,
                        wordscra.1.player.word4_2,
                        wordscra.1.player.word4_3,
                        wordscra.1.player.word4_4,
                        wordscra.1.player.word4_5),
         word5 = paste0(wordscra.1.player.word5_1,
                        wordscra.1.player.word5_2,
                        wordscra.1.player.word5_3,
                        wordscra.1.player.word5_4,
                        wordscra.1.player.word5_5),
         word6 = paste0(wordscra.1.player.word6_1,
                        wordscra.1.player.word6_2,
                        wordscra.1.player.word6_3,
                        wordscra.1.player.word6_4),
         word1f = ifelse(word1 == tools::toTitleCase(tolower("stock")), 1, 0),
         word3f = ifelse(word3 == tools::toTitleCase(tolower("broker")), 1, 0),
         word4f = ifelse(word4 == tools::toTitleCase(tolower("money")), 1, 0),
         word6f = ifelse(word6 == tools::toTitleCase(tolower("bond")), 1, 0),
         wordsf = word1f + word3f + word4f + word6f,
         lies = choice1 + choice2 + choice3 + choice4 + choice5,
         beliefs = belief1/100 + belief2/100 + belief3/100 + belief4/100 + belief5/100
  ) %>%  
  select(-starts_with("participant."),
         -starts_with("session."),
         -starts_with("postexp"),
         -starts_with("tt."),
         -starts_with("tt_norms."),
         -starts_with("bt."),
         -starts_with("wordscra."),
         -starts_with("redirect.")) %>%
  arrange(session, context, subject) %>%
  group_by(context)

save(tt_pf, file="_tt_pf.RData")
```


## Reshape and merge

### Reshape data

```{r warning=FALSE}
tt_stud_reshaped <- tt_stud %>%
  gather(cost, choice, choice1:choice5, belief1:belief5)
tt_stud_reshaped <- tt_stud_reshaped %>%
  extract(cost, c("question", "cost"), "(choice|belief)(.)")%>% 
  mutate(
    treatment = ifelse(context == "financial", "sh_sev_fin",
                       ifelse(context == "neutral", "su_ha_neu",
                              "su_ha_abs")))

tt_before_reshaped <- tt_before %>%
  gather(cost, choice, choice1:choice5, belief1:belief5)
tt_before_reshaped <- tt_before_reshaped %>%
  extract(cost, c("question", "cost"), "(choice|belief)(.)")%>% 
  mutate(
    treatment = ifelse(context == "financial", "sh_sev_fin",
                       ifelse(context == "neutral", "su_ha_neu",
                              "su_ha_abs")))

tt_pf_reshaped <- tt_pf %>%
  gather(cost, choice, choice1:choice5, belief1:belief5)
tt_pf_reshaped <- tt_pf_reshaped %>%
  extract(cost, c("question", "cost"), "(choice|belief)(.)") %>% 
  mutate(
    treatment = ifelse(is.na(treatment),
                       ifelse(context == "financial", "sh_sev_fin",
                              ifelse(context == "neutral", "su_ha_neu",
                                     ifelse(context == "abstract", "su_ha_abs", context))),
                       as.character(treatment))
    )

```

### Merge STUD and PROF data

```{r message=FALSE, warning=FALSE}
tt_before$prof <- rep(1, nrow(tt_before))
norms_before$prof <- rep(1, nrow(norms_before))
tt_stud$prof <- rep(0, nrow(tt_stud))
norms_stud$prof <- rep(0, nrow(norms_stud))
norms_studprof$prof <- rep(2, nrow(norms_studprof))
tt_pf$prof <- rep(3, nrow(tt_pf))

tt_before$prof1 <- rep(1, nrow(tt_before))
norms_before$prof1 <- rep(1, nrow(norms_before))
tt_stud$prof1 <- rep(0, nrow(tt_stud))
norms_stud$prof1 <- rep(0, nrow(norms_stud))
norms_studprof$prof1 <- rep(0, nrow(norms_studprof))
tt_pf$prof1 <- rep(1, nrow(tt_pf))

tt_stud <- tt_stud %>% 
  mutate(
    treatment = ifelse(is.na(treatment),
                       ifelse(context == "financial", "sh_sev_fin",
                              ifelse(context == "neutral", "su_ha_neu",
                                     ifelse(context == "abstract", "su_ha_abs",
context))),
                       as.character(treatment))
    )
tt_stud$treatment <- factor(tt_stud$treatment)


tt <- rbind(tt_before, tt_stud, tt_pf)
norms <- rbind(norms_before, norms_stud, norms_studprof)

tt <- tt %>% 
  mutate(
    treatment = ifelse(is.na(treatment),
                       ifelse(context == "financial", "sh_sev_fin",
                              ifelse(context == "neutral", "su_ha_neu",
                                     ifelse(context == "abstract", "su_ha_abs", context))),
                       as.character(treatment))
    )
tt$treatment <- factor(tt$treatment)

norms <- norms %>% 
  mutate(
    treatment = ifelse(context == "financial", "sh_sev_fin",
                       ifelse(context == "neutral", "su_ha_neu",
                              ifelse(context == "abstract", "su_ha_abs", context))),
    treatment)
norms$treatment <- factor(norms$treatment)


tt <- tt %>% 
  mutate(
    job1 = ifelse(job == 0, "Portfolio Manager",
                           ifelse(job == 1, "Research Analyst",
                                  ifelse(job == 2, "Consultant",
                                         ifelse(job == 3, "Financial Advisor",
                                                ifelse(job == 4, "Chief-Level Executive",
                                                       ifelse(job == 5, "Trader",
                                                              ifelse(job == 6, "Fund Manager",
                                                                     ifelse(job == 7, "Investment Managent",
                                                                            "Other"))))))))   
  )

norms <- norms %>% 
  mutate(
    job1 = ifelse(job == 0, "Portfolio Manager",
                           ifelse(job == 1, "Research Analyst",
                                  ifelse(job == 2, "Consultant",
                                         ifelse(job == 3, "Financial Advisor",
                                                ifelse(job == 4, "Chief-Level Executive",
                                                       ifelse(job == 5, "Trader",
                                                              ifelse(job == 6, "Fund Manager",
                                                                     ifelse(job == 7, "Investment Managent",
                                                                            "Other"))))))))   
  )


save(tt, file = "_tt.RData")
save(norms, file = "_norms.RData")
```


### Reshape pooled tt and norms

TT
```{R}
reshaped <- tt %>%
  gather(cost, choice, choice1:choice5, belief1:belief5)
reshaped <- reshaped %>%
  extract(cost, c("question", "cost"), "(choice|belief)(.)")
reshaped <- reshaped %>%
  spread(question, choice)

reshaped$belief <- reshaped$belief/100
reshaped$cost <- as.numeric(reshaped$cost) * (-1) + 5

save(reshaped, file = "_reshaped.RData")
```

Norms
```{R}
reshaped_norms <- norms %>%
  select(-norms_false, -norms_true) %>%
  gather(cost, choice, norms_true1:norms_false5, norms_false1:norms_false5, belief1:belief5)
reshaped_norms <- reshaped_norms %>%
  extract(cost, c("question", "cost"), "(norms_false|norms_true|belief)(.)")
reshaped_norms <- reshaped_norms %>%
  spread(question, choice) %>%
  mutate(norms = (norms_true + norms_false)/2)

reshaped_norms$belief <- reshaped_norms$belief/100
reshaped_norms$cost <- as.numeric(reshaped_norms$cost) * (-1) + 5

save(reshaped_norms, file = "_reshaped_norms.RData")
```


### Merge

```{R}
reshaped$treatment1 <- factor(reshaped$treatment,
                              levels = c('sh_sev_fin',
                                         'sh_ha_fin',
                                         'su_ha_neu',
                                         'su_sev_fin',
                                         'su_ha_abs',
                                         'su_ha_fin'))

reshaped_norms$treatment1 <- factor(reshaped_norms$treatment,
                              levels = c('sh_sev_fin',
                                         'sh_ha_fin',
                                         'su_ha_neu',
                                         'su_sev_fin',
                                         'su_ha_abs',
                                         'su_ha_fin'))

merge <- left_join(reshaped,
                   reshaped_norms %>%
                     group_by(prof, treatment1, cost) %>%
                     summarise(norms_false = mean(norms_false),
                               norms_true = mean(norms_true),
                               norms_belief = mean(belief),
                               prof1 = mean(prof1)) %>% 
                     na.omit(),
                   by=c("treatment1", "cost"),
                   suffix = c(".tt", ".norms")) %>% 
  filter(!is.na(prof.norms))

merge <- merge %>% mutate(norm = ifelse(choice==0, norms_true, norms_false))

save(merge, file = "_merge.RData")
```



# Analysis

## Table 2

Proportion  of  dishonest  reports  for  financial  professionals  and  students across treatments

```{r}
tt %>% 
  group_by(prof1, treatment) %>% 
  summarise(Pct = 1 - mean(lies, na.rm=TRUE)/5,
            sd = sd(lies/5, na.rm=TRUE),
            n = n()) %>%
  pivot_wider(names_from = prof1,
              values_from = c(Pct, sd, n)) %>%
  select(treatment,
         Pct_1, sd_1, n_1,
         Pct_0, sd_0, n_0)

```


Fisher's exact tests for differences between treatments and subject pools in Table 2

```{r}

fisher.test(t(tt %>%
                filter(treatment == "su_ha_abs") %>% 
                mutate(truths = 5 - lies) %>%
                group_by(prof1) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))

fisher.test(tt %>%
    filter(treatment == "su_ha_abs") %>% 
    mutate(truths = 5 - lies) %>%
    group_by(prof1, truths) %>%
    summarise(n = n()) %>% 
    pivot_wider(names_from = prof1, values_from = n) %>% 
    select(`0`, `1`) %>% 
    mutate(`0` = ifelse(is.na(`0`), 0, `0`)))

fisher.test(t(tt %>%
                filter(treatment == "su_ha_neu") %>% 
                mutate(truths = 5 - lies) %>%
                group_by(prof1) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))

fisher.test(t(tt %>%
                filter(treatment == "sh_sev_fin") %>% 
                mutate(truths = 5 - lies) %>%
                group_by(prof1) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))



fisher.test(t(tt %>%
                filter(treatment == "su_ha_abs" | treatment == "su_ha_neu", 
                     prof1 == 1) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(treatment) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))

fisher.test(t(tt %>%
                filter(treatment == "su_ha_neu" | treatment == "sh_sev_fin", 
                     prof1 == 1) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(treatment) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))

fisher.test(t(tt %>%
                filter(treatment == "su_ha_neu" | treatment == "sh_ha_fin", 
                     prof1 == 1) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(treatment) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))

fisher.test(t(tt %>%
                filter(treatment == "su_ha_neu" | treatment == "su_ha_fin", 
                     prof1 == 1) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(treatment) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))

fisher.test(t(tt %>%
                filter(treatment == "su_ha_neu" | treatment == "su_sev_fin", 
                     prof1 == 1) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(treatment) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))

fisher.test(t(tt %>%
                filter(treatment == "su_ha_abs" | treatment == "sh_sev_fin", 
                     prof1 == 1) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(treatment) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))

fisher.test(t(tt %>%
                filter(treatment == "su_ha_abs" | treatment == "sh_ha_fin", 
                     prof1 == 1) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(treatment) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))

fisher.test(t(tt %>%
                filter(treatment == "su_ha_abs" | treatment == "su_ha_fin", 
                     prof1 == 1) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(treatment) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))

fisher.test(t(tt %>%
                filter(treatment == "su_ha_abs" | treatment == "su_sev_fin", 
                     prof1 == 1) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(treatment) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))


fisher.test(t(tt %>%
                filter((treatment == "su_ha_abs" & prof1 == 0) | 
                        (treatment == "sh_ha_fin" & prof1 == 1)) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(prof1) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))
fisher.test(t(tt %>%
                filter((treatment == "su_ha_abs" & prof1 == 0) | 
                        (treatment == "su_ha_fin" & prof1 == 1)) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(prof1) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))
fisher.test(t(tt %>%
                filter((treatment == "su_ha_abs" & prof1 == 0) | 
                        (treatment == "su_sev_fin" & prof1 == 1)) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(prof1) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))

fisher.test(t(tt %>%
                filter((treatment == "su_ha_neu" & prof1 == 0) | 
                        (treatment == "sh_ha_fin" & prof1 == 1)) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(prof1) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))
fisher.test(t(tt %>%
                filter((treatment == "su_ha_neu" & prof1 == 0) | 
                        (treatment == "su_ha_fin" & prof1 == 1)) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(prof1) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))
fisher.test(t(tt %>%
                filter((treatment == "su_ha_neu" & prof1 == 0) | 
                        (treatment == "su_sev_fin" & prof1 == 1)) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(prof1) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))


fisher.test(t(tt %>%
                filter((treatment == "sh_sev_fin" & prof1 == 0) | 
                        (treatment == "sh_ha_fin" & prof1 == 1)) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(prof1) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))
fisher.test(t(tt %>%
                filter((treatment == "sh_sev_fin" & prof1 == 0) | 
                        (treatment == "su_ha_fin" & prof1 == 1)) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(prof1) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))
fisher.test(t(tt %>%
                filter((treatment == "sh_sev_fin" & prof1 == 0) | 
                        (treatment == "su_sev_fin" & prof1 == 1)) %>% 
                mutate(truths = 5 - lies) %>%
                group_by(prof1) %>%
                summarise(lies = sum(lies), truths = sum(truths)) %>%
                drop_na() %>%
                ungroup() %>%
                select(lies, truths)))

```


Wilcoxon rank sum tests for differences between treatments and subject pools in Table 2

```{r}

wilcox.test(lies ~ treatment,
            data = tt %>% 
              filter(treatment == "su_ha_abs" | treatment == "su_ha_neu", 
                     prof1 == 1)
            )

wilcox.test(lies ~ treatment,
            data = tt %>% 
              filter(treatment == "su_ha_abs" | treatment == "sh_sev_fin", 
                     prof1 == 1)
            )

wilcox.test(lies ~ treatment,
            data = tt %>% 
              filter(treatment == "su_ha_neu" | treatment == "sh_sev_fin", 
                     prof1 == 1)
            )

wilcox.test(lies ~ treatment,
            data = tt %>% 
              filter(treatment == "su_ha_abs" | treatment == "su_ha_fin", 
                     prof1 == 1)
            )

wilcox.test(lies ~ treatment,
            data = tt %>% 
              filter(treatment == "su_ha_neu" | treatment == "su_sev_fin", 
                     prof1 == 1)
            )

wilcox.test(lies ~ treatment,
            data = tt %>% 
              filter(treatment == "su_ha_neu" | treatment == "sh_ha_fin", 
                     prof1 == 1)
            )

wilcox.test(lies ~ treatment,
            data = tt %>% 
              filter(treatment == "su_ha_neu" | treatment == "su_ha_fin", 
                     prof1 == 1)
            )

wilcox.test(lies ~ prof1,
            data = tt %>% 
              filter(treatment == "su_ha_abs")
            )

wilcox.test(lies ~ prof1,
            data = tt %>% 
              filter(treatment == "su_ha_neu")
            )

wilcox.test(lies ~ prof1,
            data = tt %>% 
              filter(treatment == "sh_sev_fin")
            )


wilcox.test(lies ~ prof1,
            data = tt %>% 
              filter((treatment == "su_ha_abs" & prof1 == 0) | 
                        (treatment == "sh_ha_fin" & prof1 == 1))
            )

wilcox.test(lies ~ prof1,
            data = tt %>% 
              filter((treatment == "su_ha_abs" & prof1 == 0) | 
                        (treatment == "su_ha_fin" & prof1 == 1))
            )

wilcox.test(lies ~ prof1,
            data = tt %>% 
              filter((treatment == "su_ha_abs" & prof1 == 0) | 
                        (treatment == "su_sev_fin" & prof1 == 1))
            )

wilcox.test(lies ~ prof1,
            data = tt %>% 
              filter((treatment == "su_ha_neu" & prof1 == 0) | 
                        (treatment == "sh_ha_fin" & prof1 == 1))
            )

wilcox.test(lies ~ prof1,
            data = tt %>% 
              filter((treatment == "su_ha_neu" & prof1 == 0) | 
                        (treatment == "su_ha_fin" & prof1 == 1))
            )

wilcox.test(lies ~ prof1,
            data = tt %>% 
              filter((treatment == "su_ha_neu" & prof1 == 0) | 
                        (treatment == "su_sev_fin" & prof1 == 1))
            )

wilcox.test(lies ~ prof1,
            data = tt %>% 
              filter((treatment == "sh_sev_fin" & prof1 == 0) | 
                        (treatment == "sh_ha_fin" & prof1 == 1))
            )

wilcox.test(lies ~ prof1,
            data = tt %>% 
              filter((treatment == "sh_sev_fin" & prof1 == 0) | 
                        (treatment == "su_ha_fin" & prof1 == 1))
            )

wilcox.test(lies ~ prof1,
            data = tt %>% 
              filter((treatment == "sh_sev_fin" & prof1 == 0) | 
                        (treatment == "su_sev_fin" & prof1 == 1))
            )


```


Treatment differences in STUD

```{r warning=FALSE}
# Wilcoxon rank sum test: abstract vs. neutral
wilcox.test(lies ~ treatment, data = tt %>% filter(prof1 == 0, treatment != "sh_sev_fin"))

# Wilcoxon rank sum test: abstract vs. financial
wilcox.test(lies ~ treatment, data = tt %>% filter(prof1 == 0, treatment != "su_ha_neu"))

# Wilcoxon rank sum test: neutral vs. financial
wilcox.test(lies ~ treatment, data = tt %>% filter(prof1 == 0, treatment != "su_ha_abs"))

# Kruskal-Wallis test
kruskal.test(lies ~ as.factor(treatment), data = tt %>% filter(prof1 == 0))

# Fisher's exact test
test <- tt %>%
  filter(prof1 == 0) %>% 
  mutate(truths = 5 - lies) %>% 
  group_by(treatment) %>% 
  summarise(lies = sum(lies), truths = sum(truths)) %>% 
  drop_na() %>% 
  ungroup() %>% 
  select(lies, truths)
fisher.test(test)
fisher.test(t(test))

```


Treatment differences in STUD

```{r warning=FALSE}
# Wilcoxon rank sum test: abstract vs. neutral
wilcox.test(lies ~ context, data = tt_stud %>% filter(context != "financial"))

# Wilcoxon rank sum test: abstract vs. financial
wilcox.test(lies ~ context, data = tt_stud %>% filter(context != "neutral"))

# Wilcoxon rank sum test: neutral vs. financial
wilcox.test(lies ~ context, data = tt_stud %>% filter(context != "abstract"))

# Kruskal-Wallis test
kruskal.test(lies ~ as.factor(treatment), data = tt_stud)
```


Treatment differences in PROF

```{r warning=FALSE}
# Wilcoxon rank sum test: abstract vs. neutral
wilcox.test(lies ~ treatment, data = tt %>% 
              filter(prof1==1,
                     treatment == "su_ha_abs" | treatment == "su_ha_neu"))

# Wilcoxon rank sum test: abstract vs. financial
wilcox.test(lies ~ treatment, data = tt %>% 
              filter(prof1==1,
                     treatment == "su_ha_abs" | treatment == "sh_sev_fin"))

# Wilcoxon rank sum test: neutral vs. financial
wilcox.test(lies ~ treatment, data = tt %>% 
              filter(prof1==1,
                     treatment == "sh_sev_fin" | treatment == "su_ha_neu"))
```


## Table B1

Proportion of dishonest reports per subject pool across treatments

```{r}
tt %>% 
  group_by(prof, treatment) %>% 
  summarise(Pct = 1 - mean(lies, na.rm=TRUE)/5,
            sd = sd(lies/5, na.rm=TRUE),
            n = n()) %>%
  pivot_wider(names_from = prof,
              values_from = c(Pct, sd, n)) %>%
  select(treatment,
         Pct_1, sd_1, n_1,
         Pct_3, sd_3, n_3,
         Pct_0, sd_0, n_0)

```


Wilcoxon rank sum tests for differences between subject pools in Table B1

```{r}
wilcox.test(lies ~ prof,
            data = tt %>% filter(treatment == "sh_sev_fin", prof > 0))
wilcox.test(lies ~ prof,
            data = tt %>% filter(treatment == "su_ha_abs", prof > 0))
wilcox.test(lies ~ prof,
            data = tt %>% filter(treatment == "su_ha_neu", prof > 0))

wilcox.test(lies ~ prof,
            data = tt %>% filter(treatment == "sh_sev_fin", prof != 3))
wilcox.test(lies ~ prof,
            data = tt %>% filter(treatment == "su_ha_abs", prof != 3))
wilcox.test(lies ~ prof,
            data = tt %>% filter(treatment == "su_ha_neu", prof != 3))

wilcox.test(lies ~ prof,
            data = tt %>% filter(treatment == "sh_sev_fin", prof != 1))
wilcox.test(lies ~ prof,
            data = tt %>% filter(treatment == "su_ha_abs", prof != 1))
wilcox.test(lies ~ prof,
            data = tt %>% filter(treatment == "su_ha_neu", prof != 1))

```


## Table B9

Subject demographics

```{r}
demographics_prof0_mean <- tt %>% 
  ungroup() %>% 
  filter(prof == 0,
         age <= 100) %>% 
  summarise(n = n(), 
            risk = mean(risk),
            age = mean(age), 
            female = mean(female), 
            invest = mean(investment)) %>% 
  pivot_longer(-n, names_to = "Variable", values_to = "Mean PROF0")

demographics_prof0_sd <- tt %>% 
  ungroup() %>% 
  filter(prof == 0,
         age <= 100) %>% 
  summarise(n = n(), 
            risk = sd(risk),
            age = sd(age), 
            female = sd(female), 
            invest = sd(investment)) %>% 
  pivot_longer(-n, names_to = "Variable", values_to = "SD PROF0")

demographics_prof1_mean <- tt %>% 
  ungroup() %>% 
  filter(prof == 1) %>% 
  summarise(n = n(), 
            risk = mean(risk),
            age = mean(age), 
            female = mean(female), 
            invest = mean(investment)) %>% 
  pivot_longer(-n, names_to = "Variable", values_to = "Mean PROF1")

demographics_prof1_sd <- tt %>% 
  ungroup() %>% 
  filter(prof == 1) %>% 
  summarise(n = n(), 
            risk = sd(risk),
            age = sd(age), 
            female = sd(female), 
            invest = sd(investment)) %>% 
  pivot_longer(-n, names_to = "Variable", values_to = "SD PROF1")

demographics_prof3_mean <- tt %>% 
  ungroup() %>% 
  filter(prof == 3,
         age <= 100) %>% 
  summarise(n = n(), 
            risk = mean(risk),
            age = mean(age), 
            female = mean(female), 
            invest = mean(investment)) %>% 
  pivot_longer(-n, names_to = "Variable", values_to = "Mean PROF3")

demographics_prof3_sd <- tt %>% 
  ungroup() %>% 
  filter(prof == 3,
         age <= 100) %>% 
  summarise(n = n(), 
            risk = sd(risk),
            age = sd(age), 
            female = sd(female), 
            invest = sd(investment)) %>% 
  pivot_longer(-n, names_to = "Variable", values_to = "SD PROF3")

demographics_prof0norms_mean <- norms %>% 
  ungroup() %>% 
  filter(prof == 0,
         age <= 100) %>% 
  summarise(n = n(), 
            risk = mean(risk),
            age = mean(age), 
            female = mean(female), 
            invest = mean(investment)) %>% 
  pivot_longer(-n, names_to = "Variable", values_to = "Mean PROF0norms")

demographics_prof0norms_sd <- norms %>% 
  ungroup() %>% 
  filter(prof == 0,
         age <= 100) %>% 
  summarise(n = n(), 
            risk = sd(risk),
            age = sd(age), 
            female = sd(female), 
            invest = sd(investment)) %>% 
  pivot_longer(-n, names_to = "Variable", values_to = "SD PROF0norms")

demographics_prof1norms_mean <- norms %>% 
  ungroup() %>% 
  filter(prof == 1,
         age <= 100) %>% 
  summarise(n = n(), 
            risk = mean(risk),
            age = mean(age), 
            female = mean(female), 
            invest = mean(investment)) %>% 
  pivot_longer(-n, names_to = "Variable", values_to = "Mean PROF1norms")

demographics_prof1norms_sd <- norms %>% 
  ungroup() %>% 
  filter(prof == 1,
         age <= 100) %>% 
  summarise(n = n(), 
            risk = sd(risk),
            age = sd(age), 
            female = sd(female), 
            invest = sd(investment)) %>% 
  pivot_longer(-n, names_to = "Variable", values_to = "SD PROF1norms")

demographics_prof2norms_mean <- norms %>% 
  ungroup() %>% 
  filter(prof == 2,
         age <= 100) %>% 
  summarise(n = n(), 
            risk = mean(risk),
            age = mean(age), 
            female = mean(female), 
            invest = mean(investment)) %>% 
  pivot_longer(-n, names_to = "Variable", values_to = "Mean PROF2norms")

demographics_prof2norms_sd <- norms %>% 
  ungroup() %>% 
  filter(prof == 2,
         age <= 100) %>% 
  summarise(n = n(), 
            risk = sd(risk),
            age = sd(age), 
            female = sd(female), 
            invest = sd(investment)) %>% 
  pivot_longer(-n, names_to = "Variable", values_to = "SD PROF2norms")

demographics_prof <- demographics_prof1_mean %>% 
  left_join(demographics_prof1_sd) %>% 
  left_join(demographics_prof3_mean, by = c("Variable")) %>% 
  left_join(demographics_prof3_sd, by = c("Variable")) %>%
  left_join(demographics_prof1norms_mean, by = c("Variable")) %>% 
  left_join(demographics_prof1norms_sd, by = c("Variable")) %>%
  select(-starts_with("n"))

demographics_stud <- demographics_prof0_mean %>% 
  left_join(demographics_prof0_sd) %>% 
  left_join(demographics_prof0norms_mean, by = c("Variable")) %>% 
  left_join(demographics_prof0norms_sd, by = c("Variable")) %>%
  left_join(demographics_prof2norms_mean, by = c("Variable")) %>% 
  left_join(demographics_prof2norms_sd, by = c("Variable")) %>%
  select(-starts_with("n"))

demographics_prof %>%
  kable(format = "latex", 
        booktabs = T, 
        caption = "Demographics", 
        digits = 3) %>% 
  kable_styling(latex_options = c("hold_position"),
                full_width = T)

demographics_stud %>%
  kable(format = "latex", 
        booktabs = T, 
        caption = "Demographics", 
        digits = 3) %>% 
  kable_styling(latex_options = c("hold_position"),
                full_width = T)

```

```{r}
tt_before %>% 
  ungroup() %>% 
  group_by(prof, education) %>% 
  summarise(Prop = round(n()/115, 3))

tt_pf %>% 
  ungroup() %>% 
  group_by(prof, education) %>% 
  summarise(Prop = round(n()/300, 3))

norms_before %>% 
  ungroup() %>% 
  group_by(prof, education) %>% 
  summarise(Prop = round(n()/45, 3))

tt_stud %>% 
  ungroup() %>% 
  group_by(education) %>% 
  summarise(Prop = round(n()/166, 3))

norms_stud %>% 
  ungroup() %>% 
  group_by(education) %>% 
  summarise(Prop = round(n()/70, 3))

tt %>%
  filter(prof==1) %>% 
  ungroup() %>% 
  group_by(job1) %>% 
  summarise(Prop = round(n()/115, 3))

tt %>%
  filter(prof==3) %>% 
  ungroup() %>% 
  group_by(job1) %>% 
  summarise(Prop = round(n()/300, 3))

norms %>%
  filter(prof==1) %>% 
  ungroup() %>% 
  group_by(job1) %>% 
  summarise(Prop = round(n()/115, 3))


```



## Figure 1

Percentage of dishonest reports as a function of the economic costs of honesty for financial professionals and students.

```{R}
tt_stud_reshaped$treatment1 <- factor(tt_stud_reshaped$treatment, levels = c('sh_sev_fin', 'su_ha_neu', 'su_ha_abs'))
options(repr.plot.width  = 8,
        repr.plot.height = 6)
ggplot(tt_stud_reshaped %>%
         filter(question=="choice") %>%
         mutate(cost = (as.numeric(cost) * (-1) + 5),
                choice = 100-choice*100) %>%         
         group_by(cost, treatment1) %>%
         summarise(choice=mean(choice)),
       aes(x=cost, y=choice, group=treatment1,
           shape=treatment1, color=treatment1)) + 
  geom_line(aes(color=treatment1, linetype=treatment1), size=2) + 
  geom_point(lwd = 2.7) + 
  labs(x="Economic cost of honesty",
       y="Percentage of honest reports") + 
  theme_bw() +  
  theme(text = element_text(size = 20)) +   
  theme(legend.position="bottom",
        legend.key.width = unit(3, "line"),
        legend.title = element_blank(),
        panel.grid.minor.x = element_blank()) + 
  scale_linetype_manual(guide = 'legend', name="Treatment", 
                        values = c("solid",
                                   "dashed",
                                   "dotdash"),
                        labels = c(expression(FIN),
                                   expression(NEU),
                                   expression(ABS))) + 
  scale_color_manual(guide = 'legend', name="Treatment", 
                     values=viridis(n = 6)[c(1, 3, 5)],
                     labels = c(expression(FIN), 
                                expression(NEU), 
                                expression(ABS))) + 
  scale_shape_discrete(guide="legend", name="Treatment",
                       labels = c(expression(FIN),
                                  expression(NEU),
                                  expression(ABS))) +     
  ylim(0, 100) + 
  labs(title = "STUD")
ggsave("../git_data/graphs/PercLies_STUD.pdf", width=20, height=15, units="cm")
```

```{r}
tt_before_reshaped$treatment1 <- factor(tt_before_reshaped$treatment, levels = c('sh_sev_fin', 'su_ha_neu', 'su_ha_abs'))
tt_pf_reshaped$treatment1 <- factor(tt_pf_reshaped$treatment, levels = c('sh_sev_fin', 'su_ha_neu', 'su_ha_abs'))
options(repr.plot.width  = 8,
        repr.plot.height = 6)
ggplot(rbind(tt_before_reshaped, tt_pf_reshaped) %>%
         filter(question=="choice",
                treatment=="su_ha_neu"|treatment=="su_ha_abs"|treatment=="sh_sev_fin") %>%
         mutate(cost = ((as.numeric(cost) * (-1) + 5)*2),
                choice = 100 - choice*100) %>%         
         group_by(cost, treatment1) %>%
         summarise(choice=mean(choice)),
       aes(x=cost, y=choice, group=treatment1,
           shape=treatment1, color=treatment1)) + 
  geom_line(aes(color=treatment1, linetype=treatment1), size=2) + 
  geom_point(lwd = 2.7) + 
  labs(x="Economic cost of honesty",
       y="Percentage of honest reports") + 
  theme_bw() +  
  theme(text = element_text(size = 20)) +   
  theme(legend.position="bottom",
        legend.key.width = unit(3, "line"),
        legend.title = element_blank(),
        panel.grid.minor.x = element_blank()) + 
  scale_linetype_manual(guide = 'legend', name="Treatment", 
                        values = c("solid",
                                   "dashed",
                                   "dotdash"),
                        labels = c(expression(FIN),
                                   expression(NEU),
                                   expression(ABS))) + 
  scale_color_manual(guide = 'legend', name="Treatment", 
                     values=viridis(n = 6)[c(1, 3, 5)],
                     labels = c(expression(FIN), 
                                expression(NEU),
                                expression(ABS))) + 
  scale_shape_discrete(guide="legend", name="Treatment",
                       labels = c(expression(FIN),
                                  expression(NEU),
                                  expression(ABS))) +   
  ylim(0, 100) + 
  labs(title = "PROF")
ggsave("../git_data/graphs/PercLies_PROF3treat.pdf", width=20, height=15, units="cm")
```


## Figure 2

```{r}
tt_before_reshaped$treatment1 <- factor(tt_before_reshaped$treatment, levels = c('sh_sev_fin', 'sh_ha_fin', 'su_ha_neu',
                                                                         'su_sev_fin', 'su_ha_abs', 'su_ha_fin'))
tt_pf_reshaped$treatment1 <- factor(tt_pf_reshaped$treatment, levels = c('sh_sev_fin', 'sh_ha_fin', 'su_ha_neu',
                                                                         'su_sev_fin', 'su_ha_abs', 'su_ha_fin'))
options(repr.plot.width  = 8,
        repr.plot.height = 6)
ggplot(rbind(tt_before_reshaped, tt_pf_reshaped) %>%
         filter(question=="choice") %>%
         mutate(cost = (as.numeric(cost) * (-1) + 5) * 2,
                choice = 100 - choice*100) %>%         
         group_by(cost, treatment1) %>%
         summarise(choice=mean(choice)),
       aes(x=cost, y=choice, group=treatment1,
           shape=treatment1, color=treatment1)) + 
  geom_line(aes(color=treatment1, linetype=treatment1), size=2) + 
  geom_point(lwd = 2.7) + 
  labs(x="Economic cost of honesty",
       y="Percentage of honest reports") + 
  theme_bw() +  
  theme(text = element_text(size = 20)) +   
  theme(legend.position="bottom",
        legend.key.width = unit(3, "line"),
        legend.title = element_blank(),
        panel.grid.minor.x = element_blank()) + 
  scale_linetype_manual(guide = 'legend', name="Treatment", 
                        values = c("solid",
                                   "twodash",
                                   "dashed",
                                   "dotted",
                                   "dotdash",
                                   "12345678"),
                        labels = c(expression(FIN),
                                   expression(FIN[HA]^MANY),
                                   expression(NEU),
                                   expression(FIN[SEV]^ONE),
                                   expression(ABS),
                                   expression(FIN[HA]^ONE))) + 
  scale_color_manual(guide = 'legend', name="Treatment", 
                     values=viridis(n = 6),
                     labels = c(expression(FIN),
                                expression(FIN[HA]^MANY),
                                expression(NEU),
                                expression(FIN[SEV]^ONE),
                                expression(ABS),
                                expression(FIN[HA]^ONE))) + 
  scale_shape_manual(guide="legend", name="Treatment",
                       values=c(16, 1, 17,  5, 15, 6),
                       labels = c(expression(FIN),
                                  expression(FIN[HA]^MANY),
                                  expression(NEU),
                                  expression(FIN[SEV]^ONE),
                                  expression(ABS),
                                  expression(FIN[HA]^ONE))) +
  ylim(0, 100) + 
  labs(title = "PROF")
ggsave("../git_data/graphs/PercLies_PROF6treat.pdf", width=20, height=15, units="cm")
```


## Table B4

Linear estimation of the probability of an honest report for financial pro-
fessionals and students

```{R message=FALSE, warning=FALSE}
reshaped$treatment1 <- factor(reshaped$treatment, levels = c('su_ha_abs', 'su_ha_neu', 'sh_sev_fin',
                                                             'su_ha_fin', 'sh_ha_fin', 'su_sev_fin'))

reshaped$choice1 <- 1 - reshaped$choice

reg1cl <- felm(choice1 ~ as.numeric(cost) + treatment1|0|0|subject, data = reshaped %>% 
                 filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
reg2cl <- felm(choice1 ~ as.numeric(cost) + treatment1 + prof1|0|0|subject, data = reshaped %>% 
                 filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
reg3cl <- felm(choice1 ~ as.numeric(cost) + treatment1*prof1 |0|0|subject, data = reshaped %>% 
                 filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
reg4cl <- felm(choice1 ~ as.numeric(cost) + treatment1*prof1 + female + risk + age + investment +  
                 pref1_1 + pref1_2 + pref1_3 + pref1_4 + pref2_1 + pref2_2 + pref2_3 +
                 order|0|0|subject,
           data = reshaped %>% 
                 filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs')) 

stargazer(reg2cl, reg3cl, reg4cl, digits=3, align=FALSE, type="text",
         dep.var.caption = "Dependent variable: Honest report")
```

```{r}
# Wald tests for Table 3

library(car)

# NEU+PROF vs. NEU+STUD
linearHypothesis(reg3cl, "prof1 + treatment1su_ha_neu:prof1")
linearHypothesis(reg4cl, "prof1 + treatment1su_ha_neu:prof1")

# FIN+PROF vs. FIN+STUD
linearHypothesis(reg3cl, "prof1 + treatment1sh_sev_fin:prof1")
linearHypothesis(reg4cl, "prof1 + treatment1sh_sev_fin:prof1")

# ABS+PROF vs. NEU+PROF
linearHypothesis(reg3cl, "treatment1su_ha_neu + treatment1su_ha_neu:prof1")
linearHypothesis(reg4cl, "treatment1su_ha_neu + treatment1su_ha_neu:prof1")

# ABS+PROF vs. FIN+PROF
linearHypothesis(reg3cl, "treatment1sh_sev_fin + treatment1sh_sev_fin:prof1")
linearHypothesis(reg4cl, "treatment1sh_sev_fin + treatment1sh_sev_fin:prof1")

# NEU+PROF vs. FIN+PROF
linearHypothesis(reg3cl, "treatment1su_ha_neu + treatment1su_ha_neu:prof1 = treatment1sh_sev_fin + treatment1sh_sev_fin:prof1")
linearHypothesis(reg4cl, "treatment1su_ha_neu + treatment1su_ha_neu:prof1 = treatment1sh_sev_fin + treatment1sh_sev_fin:prof1")

```


## Table B6

Linear estimation of the probability of an honest report for financial profes-
sionals across different treatments.

```{r}
reshaped$choice1 <- 1 - reshaped$choice

reg5cl <- felm(choice1 ~ as.numeric(cost) + treatment1|0|0|subject, data = reshaped %>% filter(prof==1|prof==3))
reg7cl <- felm(choice1 ~ as.numeric(cost) + treatment1 + female + risk + age + investment +  
                 pref1_1 + pref1_2 + pref1_3 + pref1_4 + pref2_1 + pref2_2 + pref2_3 +
                 order|0|0|subject, data = reshaped %>% filter(prof==1|prof==3))


stargazer(reg5cl, reg7cl, digits=3, align=FALSE, type="text",
         dep.var.caption = "Dependent variable: Honest report")
```


## Table 4

Linear estimation of the proportion of honest reports for financial professionals across different treatments.

```{r}
tt$treatment1 <- factor(tt$treatment, levels = c('su_ha_abs', 'su_ha_neu', 'sh_sev_fin',
                                                             'su_ha_fin', 'sh_ha_fin', 'su_sev_fin'))

tt$truths <- 1 - tt$lies/5

regsub5cl <- felm(truths ~ treatment1|0|0|subject, data = tt %>% filter(prof==1|prof==3))
regsub7cl <- felm(truths ~ treatment1 + female + risk + age + investment +  
                 pref1_1 + pref1_2 + pref1_3 + pref1_4 + pref2_1 + pref2_2 + pref2_3 +
                 order|0|0|subject, data = tt %>% filter(prof==1|prof==3))


stargazer(regsub5cl, regsub7cl, digits=3, align=FALSE, type="text",
         dep.var.caption = "Dependent variable: Proportion of honest reports")
```



## Table B2

```{R message=FALSE, warning=FALSE}

# ONLY BEFORE-POOL

reg1clBEFORE <- felm(choice1 ~ as.numeric(cost) + treatment1|0|0|subject, 
               data = reshaped %>%
                 filter(prof!=3,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
reg2clBEFORE <- felm(choice1 ~ as.numeric(cost) + treatment1 + prof1|0|0|subject, 
               data = reshaped %>% 
                 filter(prof!=3,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
reg3clBEFORE <- felm(choice1 ~ as.numeric(cost) + treatment1*prof1 |0|0|subject, 
               data = reshaped %>% 
                 filter(prof!=3,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
reg4clBEFORE <- felm(choice1 ~ as.numeric(cost) + treatment1*prof1 + female + risk + age + investment +  pref1_1 + pref1_2 + pref1_3 + pref1_4 + pref2_1 + pref2_2 + pref2_3 + order|0|0|subject,
               data = reshaped %>% 
                 filter(prof!=3,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs')) 

stargazer(reg1clBEFORE, reg2clBEFORE, reg3clBEFORE, reg4clBEFORE, digits=3, align=FALSE, type="text",
         dep.var.caption = "Dependent variable: Honest report")


# ONLY PROLIFIC-POOL

reg1clPF <- felm(choice1 ~ as.numeric(cost) + treatment1|0|0|subject, 
               data = reshaped %>%
                 filter(prof!=1,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
reg2clPF <- felm(choice1 ~ as.numeric(cost) + treatment1 + prof1|0|0|subject, 
               data = reshaped %>% 
                 filter(prof!=1,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
reg3clPF <- felm(choice1 ~ as.numeric(cost) + treatment1*prof1 |0|0|subject, 
               data = reshaped %>% 
                 filter(prof!=1,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
reg4clPF <- felm(choice1 ~ as.numeric(cost) + treatment1*prof1 + female + risk + age + investment +  pref1_1 + pref1_2 + pref1_3 + pref1_4 + pref2_1 + pref2_2 + pref2_3 + order|0|0|subject,
               data = reshaped %>% 
                 filter(prof!=1,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs')) 

stargazer(reg1clPF, reg2clPF, reg3clPF, reg4clPF, digits=3, align=FALSE, type="text",
         dep.var.caption = "Dependent variable: Honest report")
```

```{R message=FALSE, warning=FALSE}

tt$treatment1 <- factor(tt$treatment, levels = c('su_ha_abs', 
                                                 'su_ha_neu', 
                                                 'sh_sev_fin'))

tt$truths <- 1 - tt$lies/5

# ONLY BEFORE-POOL

regsub1clBEFORE <- felm(truths ~ treatment1|0|0|subject, 
               data = tt %>%
                 filter(prof!=3,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
regsub2clBEFORE <- felm(truths ~ treatment1 + prof1|0|0|subject, 
               data = tt %>% 
                 filter(prof!=3,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
regsub3clBEFORE <- felm(truths ~ treatment1*prof1 |0|0|subject, 
               data = tt %>% 
                 filter(prof!=3,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
regsub4clBEFORE <- felm(truths ~ treatment1*prof1 + female + risk + age + investment +  pref1_1 + pref1_2 + pref1_3 + pref1_4 + pref2_1 + pref2_2 + pref2_3 + order|0|0|subject,
               data = tt %>% 
                 filter(prof!=3,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs')) 

stargazer(regsub1clBEFORE, regsub2clBEFORE, regsub3clBEFORE, regsub4clBEFORE, digits=3, align=FALSE, type="text",
         dep.var.caption = "Dependent variable: Proportion of honest reports")


# ONLY PROLIFIC-POOL

regsub1clPF <- felm(truths ~ treatment1|0|0|subject, 
               data = tt %>%
                 filter(prof!=1,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
regsub2clPF <- felm(truths ~ treatment1 + prof1|0|0|subject, 
               data = tt %>% 
                 filter(prof!=1,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
regsub3clPF <- felm(truths ~ treatment1*prof1 |0|0|subject, 
               data = tt %>% 
                 filter(prof!=1,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
regsub4clPF <- felm(truths ~ treatment1*prof1 + female + risk + age + investment +  pref1_1 + pref1_2 + pref1_3 + pref1_4 + pref2_1 + pref2_2 + pref2_3 + order|0|0|subject,
               data = tt %>% 
                 filter(prof!=1,
                        treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs')) 

stargazer(regsub1clPF, regsub2clPF, regsub3clPF, regsub4clPF, digits=3, align=FALSE, type="text",
         dep.var.caption = "Dependent variable: Proportion of honest reports")
```


## Table B3

Ordered logit regression on the proportion of honest reports for financial professionals and students.

```{r}

tt$treatment1 <- factor(tt$treatment, levels = c('su_ha_abs', 
                                                 'su_ha_neu', 
                                                 'sh_sev_fin'))

tt$truths <- factor(1 - tt$lies/5, levels = c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0))

reg1ologit <- polr(truths ~ treatment1, Hess = TRUE,
                  data = tt %>% filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
reg1ologit.or <- exp(coef(reg1ologit))
reg2ologit <- polr(truths ~ treatment1 + prof1,  Hess = TRUE,
                  data = tt %>% filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
reg2ologit.or <- exp(coef(reg2ologit))
reg3ologit <- polr(truths ~ treatment1*prof1,  Hess = TRUE,
                  data = tt %>% filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
reg3ologit.or <- exp(coef(reg3ologit))
reg4ologit <- polr(truths ~ treatment1*prof1 + female + risk + age + investment + order +  pref1_1 + pref1_2 + pref1_3 + pref1_4 + pref2_1 + pref2_2 + pref2_3, Hess = TRUE,
                  data = tt %>% filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'))
reg4ologit.or <- exp(coef(reg4ologit))

stargazer(reg2ologit, reg3ologit, reg4ologit, type="text",
          coef = list(reg2ologit.or, reg3ologit.or, reg4ologit.or),
          dep.var.caption = "Dependent variable: Proportion of honest reports")

```


## Table B5

Logistic regression on the probability of an honest report for financial professionals and students.

```{r}

reshaped$treatment1 <- factor(reshaped$treatment, levels = c('su_ha_abs', 
                                                 'su_ha_neu', 
                                                 'sh_sev_fin'))

reshaped$choice1 <- 1 - reshaped$choice

logit1cl <- glm(choice1 ~ as.numeric(cost) + treatment1, 
                                  data = reshaped %>%
                                    filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'), family="binomial")
logit1clse <- miceadds::glm.cluster(choice1 ~ as.numeric(cost) + treatment1, 
                                  data = reshaped %>%
                                    filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'),
                                  cluster="subject", family="binomial")
logit1cl.or <- exp(coef(logit1cl))

logit2cl <- glm(choice1 ~ as.numeric(cost) + treatment1 + prof1,
                                  data = reshaped %>%
                                    filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'), family="binomial")
logit2clse <- miceadds::glm.cluster(choice1 ~ as.numeric(cost) + treatment1 + prof1,
                                  data = reshaped %>%
                                    filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'),
                                  cluster="subject", family="binomial")
logit2cl.or <- exp(coef(logit2cl))

logit3cl <- glm(choice1 ~ as.numeric(cost) + treatment1*prof1,
                                  data = reshaped %>%
                                    filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'), family="binomial")
logit3clse <- miceadds::glm.cluster(choice1 ~ as.numeric(cost) + treatment1*prof1,
                                  data = reshaped %>%
                                    filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'),
                                  cluster="subject", family="binomial")
logit3cl.or <- exp(coef(logit3cl))

logit4cl <- glm(choice1 ~ as.numeric(cost) + treatment1*prof1 + female + risk + age + investment + pref1_1 + pref1_2 + pref1_3 + pref1_4 + pref2_1 + pref2_2 + pref2_3 + order,
                                  data = reshaped %>%
                                    filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'), family="binomial")
logit4clse <- miceadds::glm.cluster(choice1 ~ as.numeric(cost) + treatment1*prof1 + female + risk + age + investment + pref1_1 + pref1_2 + pref1_3 + pref1_4 + pref2_1 + pref2_2 + pref2_3 + order,
                                  data = reshaped %>%
                                    filter(treatment1 == 'sh_sev_fin'|treatment1 == 'su_ha_neu'|treatment1 == 'su_ha_abs'),
                                  cluster="subject", family="binomial")
logit4cl.or <- exp(coef(logit4cl))

stargazer(logit2cl, logit3cl, logit4cl,
          coef = list(
            logit2cl.or,
            logit3cl.or,
            logit4cl.or
          ),
          se = list(
            as.data.frame(summary(logit2clse))[, 2],
            as.data.frame(summary(logit3clse))[, 2],
            as.data.frame(summary(logit4clse))[, 2]
          ),
          align=TRUE, type="text",
          title = "Logistic regression with standard errors clustered at the subject-level",
          dep.var.caption = "Dependent variable: Prob(Dishonest report)")
```


## Table B7

Logistic regression on the probability of an honest report for financial professionals across different treatments.

```{r}

reshaped$treatment1 <- factor(reshaped$treatment,
                              levels = c('su_ha_abs',
                                             'su_ha_neu',
                                             'sh_sev_fin',
                                             'sh_ha_fin',
                                             'su_sev_fin',
                                             'su_ha_fin'))

reshaped$choice1 <- 1 - reshaped$choice

logit5clse <- miceadds::glm.cluster(choice1 ~ as.numeric(cost) + treatment1, data = reshaped %>% filter(prof==1|prof==3),
                                  cluster = "subject",
                                  family = "binomial")

logit7clse <- miceadds::glm.cluster(choice1 ~ as.numeric(cost) + treatment1 + female + risk + age + investment + pref1_1 + pref1_2 + pref1_3 + pref1_4 + pref2_1 + pref2_2 + pref2_3 + order, data = reshaped %>% filter(prof==1|prof==3),
                                  cluster = "subject",
                                  family = "binomial")

logit5cl <- glm(choice1 ~ as.numeric(cost) + treatment1, data = reshaped %>% filter(prof==1|prof==3),
                                  family = "binomial")

logit7cl <- glm(choice1 ~ as.numeric(cost) + treatment1 + female + risk + age + investment + pref1_1 + pref1_2 + pref1_3 + pref1_4 + pref2_1 + pref2_2 + pref2_3 + order, data = reshaped %>% filter(prof==1|prof==3),
                                  family = "binomial")

logit5cl.or <- exp(coef(logit5cl))
logit7cl.or <- exp(coef(logit7cl))

stargazer(logit5cl, logit7cl,
          coef = list(
            logit5cl.or,
            logit7cl.or
          ),
          se = list(
            as.data.frame(summary(logit5clse))[, 2],
            as.data.frame(summary(logit7clse))[, 2]
          ),
          align=TRUE, type="text",
          title = "Logistic regression with standard errors clustered at the subject-level",
          dep.var.caption = "Dependent variable: Prob(Honest report)")
```


## Figure 3

Perceived severity of a lie's consequences and the influence of reputational concerns on dishonest behavior.

```{r}
tt_pf$treatment1 <- factor(tt_pf$treatment,
                              levels = rev(c('su_ha_abs',
                                             'su_ha_neu',
                                             'sh_sev_fin',
                                             'sh_ha_fin',
                                             'su_sev_fin',
                                             'su_ha_fin')))

tt_pf %>% 
  group_by(treatment1) %>% 
  summarise(Severity = mean(severity),
            Severitymax = CI(severity)[1],
            Severitymin = CI(severity)[3]) %>%
  mutate(severitytreat = ifelse(grepl("sev", treatment1), 
                                "severe", "harmless"),
         financialtreat = factor(ifelse(grepl("fin", treatment1), 1, 0))) %>% 
  ggplot(aes(x = treatment1, 
             y = Severity, 
             ymax = Severitymax,
             ymin = Severitymin,
             color = severitytreat,
             shape = financialtreat)) + 
  geom_errorbar(width=.2, lwd = 1) + 
  geom_point(lwd = 2.7) + 
  coord_flip() +   
  theme_bw(base_size = 18) + 
  theme(legend.position="bottom",
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.margin = margin(t = 0),
        legend.box.margin = margin(t = 0),
        legend.box.spacing = unit(0.3, "cm"),
        axis.title.y = element_blank(),
        panel.grid.minor.y = element_blank()) +
  scale_x_discrete(labels = rev(c(expression(ABS),
                                  expression(NEU),
                                  expression(FIN),
                                  expression(FIN[HA]^MANY),
                                  expression(FIN[SEV]^ONE),
                                  expression(FIN[HA]^ONE)))) + 
  scale_color_manual(values=viridis(n = 6)[c(1,5)]) + 
  scale_shape_manual(values = c(15, 5),
                     labels = c("non-financial", "financial")) + 
  scale_y_continuous(limits = c(1, 7),
                     breaks = seq(1, 7, 1)) +  
  ylab("Perceived severity of consequences") + 
  labs(title = "Perceived severity of consequences")
ggsave("../git_latex/graphs/Severity.pdf", width=20, height=15, units="cm")

tt_pf %>% 
  group_by(treatment1) %>% 
  summarise(Reputation = mean(reputation),
            Reputationmax = CI(reputation)[1],
            Reputationmin = CI(reputation)[3]) %>%
  mutate(financialtreat = factor(ifelse(grepl("fin", treatment1), 1, 0))) %>% 
  ggplot(aes(x = treatment1, 
             y = Reputation, 
             ymax = Reputationmax,
             ymin = Reputationmin,
             shape = financialtreat)) + 
  geom_errorbar(width=.2, lwd = 1, color = viridis(n = 6)[3]) + 
  geom_point(lwd = 2.7) + 
  coord_flip() +  
  theme_bw(base_size = 18) + 
  theme(legend.position="bottom",
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.margin = margin(t = 0),
        legend.box.margin = margin(t = 0),
        legend.box.spacing = unit(0.3, "cm"),
        axis.title.y = element_blank(),
        panel.grid.minor.y = element_blank()) +
  scale_x_discrete(labels = rev(c(expression(ABS),
                                  expression(NEU),
                                  expression(FIN),
                                  expression(FIN[HA]^MANY),
                                  expression(FIN[SEV]^ONE),
                                  expression(FIN[HA]^ONE)))) + 
  scale_shape_manual(values = c(15, 5),
                     labels = c("non-financial", "financial")) + 
  scale_y_continuous(limits = c(1, 7),
                     breaks = seq(1, 7, 1)) +  
  ylab("Influence of reputational concerns") +
  labs(title = "Reputational concerns")
ggsave("../git_latex/graphs/ReputationalConcerns.pdf", width=20, height=15, units="cm")
```


## Figure B1

Beliefs about the percentage of dishonest reports as a function of the
economic costs of honesty.

```{R}
tt_stud_reshaped$treatment1 <- factor(tt_stud_reshaped$treatment, levels = c('sh_sev_fin', 'su_ha_neu', 'su_ha_abs'))
options(repr.plot.width  = 8,
        repr.plot.height = 6)
ggplot(tt_stud_reshaped %>%
         filter(question=="belief") %>%
         mutate(cost = as.numeric(cost) * (-1) + 5) %>%                  
         group_by(cost, treatment1) %>%
         summarise(belief=100 - mean(choice)),
       aes(x=cost, y=belief, group=treatment1)) + 
  geom_line(aes(color=treatment1, linetype=treatment1), size=2) + 
  geom_point() + 
  labs(x="Economic cost of honesty",
       y="Percentage of honest reports") + 
  theme_bw() +  
  theme(text = element_text(size = 20)) +   
  theme(legend.position="bottom",
        legend.key.width = unit(3, "line"),
        legend.title = element_blank(),
        panel.grid.minor.x = element_blank()) + 
  scale_linetype_discrete(guide = 'legend', name="Treatment",
                          labels = c(expression(FIN),
                                     expression(NEU), 
                                     expression(ABS))) + 
  scale_color_manual(guide = 'legend', name="Treatment", values=viridis(n = 6)[c(1, 3, 5)],
                     labels = c(expression(FIN), 
                                expression(NEU), 
                                expression(ABS))) + 
  ylim(0, 100) + 
  labs(title = "STUD")  
ggsave("../git_data/graphs/BeliefsPercLies_STUD.pdf", width=20, height=15, units="cm")
```

```{R}
tt_before_reshaped$treatment1 <- factor(tt_before_reshaped$treatment, levels = c('sh_sev_fin', 'sh_ha_fin', 'su_ha_neu',
                                                                         'su_sev_fin', 'su_ha_abs', 'su_ha_fin'))
tt_pf_reshaped$treatment1 <- factor(tt_pf_reshaped$treatment, levels = c('sh_sev_fin', 'sh_ha_fin', 'su_ha_neu',
                                                                         'su_sev_fin', 'su_ha_abs', 'su_ha_fin'))
options(repr.plot.width  = 8,
        repr.plot.height = 6)
ggplot(rbind(tt_before_reshaped, tt_pf_reshaped) %>%
         filter(question=="belief",
                treatment=="su_ha_neu"|treatment=="su_ha_abs"|treatment=="sh_sev_fin") %>%
         mutate(cost = as.numeric(cost) * (-1) + 5) %>%                  
         group_by(cost, context) %>%
         summarise(belief=100 - mean(choice)),
       aes(x=cost, y=belief, group=context)) + 
  geom_line(aes(color=context, linetype=context), size=2) + 
  geom_point() + 
  labs(x="Economic cost of honesty",
       y="Percentage of honest reports") + 
  theme_bw() +  
  theme(text = element_text(size = 20)) +   
  theme(legend.position="bottom",
        legend.key.width = unit(3, "line"),
        legend.title = element_blank(),
        panel.grid.minor.x = element_blank()) + 
  scale_linetype_discrete(guide = 'legend', name="Treatment",
                          labels = c(expression(FIN),
                                     expression(NEU),
                                     expression(ABS))) + 
  scale_color_manual(guide = 'legend', name="Treatment", values=viridis(n = 6)[c(1, 3, 5)],
                     labels = c(expression(FIN), 
                                expression(NEU), 
                                expression(ABS))) + 
  ylim(0, 100) + 
  labs(title = "PROF") 
ggsave("../git_data/graphs/BeliefsPercLies_PROF.pdf", width=20, height=15, units="cm")
```


Correlation own lying behavior/beliefs

```{r}
cor.test(tt$lies, tt$beliefs)
```


## Figure 5

Percentage of dishonest reports as a function of expectations by a separate
groups of subjects

```{r}
normsbeliefs <- merge %>%
  filter(prof1.tt == 1) %>% 
  group_by(prof.norms, treatment1, cost) %>%
  summarise(norm = mean(norm, na.rm=TRUE), 
            normf = mean(norms_false, na.rm=TRUE), 
            normt = mean(norms_true, na.rm=TRUE), 
            choice = mean(choice, na.rm=TRUE), 
            belief = mean(norms_belief, na.rm=TRUE), n())
```

```{r message=FALSE, warning=FALSE}
normsbeliefs$treatment1 <- factor(normsbeliefs$treatment1, levels = c('sh_sev_fin', 'su_ha_neu', 'su_ha_abs'))

ggplot(normsbeliefs %>% filter(prof.norms==1), aes(x = 1 - belief, y = 1 - choice)) +
  geom_smooth(method = lm, color="grey40") +  
  geom_point(aes(color = treatment1, shape = treatment1), size = 4.2) +
  labs(x="Expected percentage of honest reports \n in the norm-elicitation experiment",
       y="Percentage of honest reports \n in the main experiment") +   
  theme_bw() +  
  theme(text = element_text(size = 20)) +   
  theme(legend.position="bottom") +   
  scale_color_manual(guide = "legend", name="", 
                     values=viridis(n = 6)[c(1, 3, 5)],
                     labels = c(expression(FIN), 
                                expression(NEU), 
                                expression(ABS))) + 
  scale_shape_manual(guide = "legend", name="",
                     values = c(19, 17, 15),
                     labels = c(expression(FIN), 
                                expression(NEU), 
                                expression(ABS))) +   
  scale_y_continuous(limits = c(0, 1), breaks=seq(0, 1, 0.25)) + 
  xlim(0, 1) + 
  labs(title = bquote("PROF")) 
ggsave("../git_data/graphs/BeliefsPercLiesExpIExpII_PROF.pdf", width=20, height=15, units="cm")
```

```{r}
1 - normsbeliefs %>% filter(prof.norms==1) %>% .$belief %>% max(na.rm=TRUE)
normsbeliefs %>% filter(prof.norms==1) %>% filter(1 - choice < 0.426875) %>% .$choice %>% length()
```

```{r}
normsbeliefsstudprof <- merge %>%
  filter(prof.norms==2) %>%
  group_by(prof.norms, treatment1, cost) %>%
  summarise(norm = mean(norm), choice = mean(choice), beliefstudprof = mean(norms_belief)) %>%
  ungroup %>%
  dplyr::select(-starts_with("prof")) %>% 
  na.omit()

normsbeliefs1 <- full_join(normsbeliefs,
                           normsbeliefsstudprof,
                           by = c("treatment1", "cost"),
                           suffix = c(".norms", ".studprof")) %>%
  na.omit()

```

```{r}
normsbeliefs1$treatment1 <- factor(normsbeliefs1$treatment1, levels = c('sh_sev_fin', 'su_ha_neu', 'su_ha_abs'))

ggplot(normsbeliefs1 %>% filter(prof.norms==1), aes(x = 1 - beliefstudprof, y = 1 - choice.norms)) +
  geom_smooth(method = lm, color="grey40") +    
  geom_point(aes(color = treatment1, shape = treatment1), size = 4.2) + 
  labs(x="Expected percentage of honest reports \n in the norm-elicitation experiment",
       y="Percentage of honest reports \n in the main experiment") +   
  theme_bw() +  
  theme(text = element_text(size = 20)) +   
  theme(legend.position="bottom") +   
  scale_color_manual(guide = "legend", name="", 
                     values=viridis(n = 6)[c(1, 3, 5)],
                     labels = c(expression(FIN), 
                                expression(NEU), 
                                expression(ABS))) + 
  scale_shape_manual(guide = "legend", name="",
                     values = c(19, 17, 15),
                     labels = c(expression(FIN), 
                                expression(NEU), 
                                expression(ABS))) +   
  scale_y_continuous(limits = c(0, 1), breaks=seq(0, 1, 0.25)) + 
  xlim(0, 1) + 
  labs(title = bquote("STUD"^"PROF"))
ggsave("../git_data/graphs/BeliefsPercLiesExpIExpII_STUDPROF.pdf", width=20, height=15, units="cm")
```


## Table B8

Decision-situation-level ordinary least squares estimation of the percentage
of dishonest reports

```{r warning=FALSE}
regbeliefsexpIexpII_stud <- lm(choice ~ belief, data = normsbeliefs %>% filter(prof.norms==0))
regbeliefsexpIexpII_prof <- lm(choice ~ belief, data = normsbeliefs %>% filter(prof.norms==1))
regbeliefsexpIexpII_studprof <- lm(choice.norms ~ beliefstudprof, data = normsbeliefs1 %>% filter(prof.norms==1))

stargazer(regbeliefsexpIexpII_prof, regbeliefsexpIexpII_studprof, regbeliefsexpIexpII_stud, type = "text", digits=3)
```

```{r}
linearHypothesis(regbeliefsexpIexpII_prof, "belief = 1")
```


## Subject-group differences in social norms

```{r warning=FALSE}
# Wilcoxon rank sum test: STUD vs. PROF for ABSTRACT
wilcox.test(norms_false ~ prof, data = norms %>% filter(prof!=2, context=="abstract"))
```

```{r warning=FALSE}
# Wilcoxon rank sum test: STUD vs. PROF for NEUTRAL
wilcox.test(norms_false ~ prof, data = norms %>% filter(prof!=2, context=="neutral"))
```

```{r warning=FALSE}
# Wilcoxon rank sum test: STUD vs. PROF for FINANCIAL
wilcox.test(norms_false ~ prof, data = norms %>% filter(prof!=2, context=="financial"))
```

```{r warning=FALSE}
# Wilcoxon rank sum test: neutral vs. financial
wilcox.test(norms_true ~ prof, data = norms %>% filter(prof!=2, context=="abstract"))
```

```{r warning=FALSE}
# Wilcoxon rank sum test: abstract vs. financial
wilcox.test(norms_true ~ prof, data = norms %>% filter(prof!=2, context=="neutral"))
```

```{r warning=FALSE}
# Wilcoxon rank sum test: abstract vs. neutral
wilcox.test(norms_true ~ prof, data = norms %>% filter(prof!=2, context=="financial"))
```

```{r warning=FALSE}
# Kruskal-Wallis test:
kruskal.test(norms_true ~ prof, data = norms)
```


## Treatment differences in social norms

```{r warning=FALSE}
# Wilcoxon rank sum test: abstract vs. neutral
wilcox.test(norms_false ~ context, data = norms %>% filter(prof==1, context!="financial"))
```

```{r warning=FALSE}
# Wilcoxon rank sum test: abstract vs. financial
wilcox.test(norms_false ~ context, data = norms %>% filter(prof==1, context!="neutral"))
```

```{r warning=FALSE}
# Wilcoxon rank sum test: neutral vs. financial
wilcox.test(norms_false ~ context, data = norms %>% filter(prof==1, context!="abstract"))
```


## Variation across economic costs of honesty

Correlation between economic costs of honesty and social appropriateness of an _honest_ report:

```{r}
cor.test(reshaped_norms$cost, reshaped_norms$norms_true)
```

Correlation between economic costs of honesty and social appropriateness of a _dishonest_ report:

```{r}
cor.test(reshaped_norms$cost, reshaped_norms$norms_false)
```


## Figure 4

```{R}
gathered <- norms %>%
  gather(key = "truefalse", value = "norms", c(norms_true, norms_false))
gathered$context1 <- factor(gathered$context, levels = c('abstract', 'neutral', 'financial'))
```

```{r}
gathered$treatment1 <- factor(gathered$context, 
                              levels = c('financial', 'neutral', 'abstract'),
                              labels = c(expression(FIN[SEV]^MANY),
                                         expression(NEU[HA]^ONE),
                                         expression(ABS[HA]^ONE)))

ggplot(data = gathered %>%
         ungroup %>%
         mutate(prof1 = ifelse(prof==2, 0.5, prof),
                prof1 = factor(prof1,
                               levels = c(0, 0.5, 1),
                               labels = c("STUD", 
                                          bquote("STUD"^"PROF"), 
                                          "PROF"))) %>%
         filter(truefalse == "norms_false") %>% 
         group_by(prof1, treatment1) %>%
         summarise(normsmax = CI(norms)[1],
                   normsmin = CI(norms)[3],
                   norms = mean(norms)),
       aes(x = factor(treatment1), y = norms,
           ymin = normsmin, ymax = normsmax,
           color=factor(treatment1), shape=factor(treatment1))) +
  geom_errorbar(width=.2, lwd = 1) +   
  geom_point(lwd = 2.7) + 
  facet_wrap( ~ prof1, labeller = label_parsed) + 
  geom_hline(yintercept = 0) + 
  labs(x="",
       y="Social approriateness \n of a dishonest report") +   
  theme_bw() + 
  theme(text = element_text(size = 16)) +     
  theme(legend.position="bottom") +
  theme(axis.text.x=element_blank()) + 
  theme(panel.spacing = unit(0, "lines")) + 
  scale_x_discrete(breaks = NULL) + 
  scale_y_continuous(breaks = scales::pretty_breaks(n = 6), limits = c(-1, 0.18)) + 
  scale_color_manual(guide="legend",
                     name="",
                     values=viridis(n = 6)[c(1,3,5)],
                     labels = c(expression(FIN),
                                         expression(NEU),
                                         expression(ABS))) + 
  scale_shape_discrete(guide="legend",
                       name="",
                       labels = c(expression(FIN),
                                         expression(NEU),
                                         expression(ABS)))
ggsave("../git_latex/graphs/Norms_lineplot.pdf", width=25, height=15, units="cm")
```


# Variable descriptions

 Variable           |   Description
 --------           |   ---------------------------------------------------------------------------------
 `subject`          |   Subject ID
 `payoff`           |   Payout from the experiment
 `session`          |   Experimental session ID
 `context`          |   Treatment (context, framed instructions): `abstract`, `neutral`, or `financial`
 `order`            |   Ascending or decreasing order of decisions (randomly drawn for each subject)
 `choice1`          |   Choice in decision 1: `0` (honest report) or `1` (dishonest report)
 `choice2`          |   Choice in decision 2: `0` (honest report) or `1` (dishonest report)
 `choice3`          |   Choice in decision 3: `0` (honest report) or `1` (dishonest report)
 `choice4`          |   Choice in decision 4: `0` (honest report) or `1` (dishonest report)
 `choice5`          |   Choice in decision 5: `0` (honest report) or `1` (dishonest report) 
 `belief1`          |   Expected percentage of dishonest reports in decision 1
 `belief2`          |   Expected percentage of dishonest reports in decision 2
 `belief3`          |   Expected percentage of dishonest reports in decision 3
 `belief4`          |   Expected percentage of dishonest reports in decision 4
 `belief5`          |   Expected percentage of dishonest reports in decision 5 
 `risk`             |   Risk preferences elicited with the general risk question, `1` (...) to `7` (...)
 `pref1_1`          |   Patience (Falk et al., 2018): `1` (completely unwilling to do so) to `7` (very willing to do so)
 `pref1_2`          |   Negative Reciprocity 1 (Falk et al., 2018): `1` (completely unwilling to do so) to `7` (very willing to do so)
 `pref1_3`          |   Negative Reciprocity 2 (Falk et al., 2018): `1` (completely unwilling to do so) to `7` (very willing to do so)
 `pref1_4`          |   Altruism (Falk et al., 2018): `1` (completely unwilling to do so) to `7` (very willing to do so)
 `pref2_1`          |   Positive Reciprocity (Falk et al., 2018): `1` (does not describe me at all) to `7` (describes me perfectly)
 `pref2_2`          |   Negative Reciprocity 3 (Falk et al., 2018): `1` (does not describe me at all) to `7` (describes me perfectly)
 `pref2_3`          |   Trust (Falk et al., 2018): `1` (does not describe me at all) to `7` (describes me perfectly)
 `age`              |   Age
 `female`           |   Gender: `0` (male) or `1` (female)
 `education`        |   Education: `0` (Compulsory school), `1` (Apprenticeship), `2` (Technical college), `3` (High school), `4` (University), or `-1` (Prefer not to say)
 `job`              |   Job (only PROF): `0` (Portfolio Manager), `1` (Research Analyst), `2` (Consultant), `3` (Financial Advisor), `4` (Chief-Level Executive), `5` (Trader), `6` (Fund Manager), `7` (Investment Managent), or `8` (Other)
 `investment`       |   Investment in financial products in the last 5 years: yes (`1`) or no (`0`)
 `whichinvestment`  |   If `investment = 1`, which financial product
 `finnews`          |   Check financial news: `4` (Daily), `3` (Several times a week), `2` (Once a week), `1` (Less than once a week), or `0` (Never)
 `tt`               |   Truth-telling task (`1`) or norm-elicitation task (`0`)
 `word1`            |   Answer to word scarambling 1
 `word2`            |   Answer to word scarambling 2
 `word3`            |   Answer to word scarambling 3
 `word4`            |   Answer to word scarambling 4
 `word5`            |   Answer to word scarambling 5
 `word6`            |   Answer to word scarambling 6
 `word1f`           |   Financial word in word scrambing 1: yes (`1`) or no (`0`)
 `word3f`           |   Financial word in word scrambing 3: yes (`1`) or no (`0`)
 `word4f`           |   Financial word in word scrambing 4: yes (`1`) or no (`0`)
 `word6f`           |   Financial word in word scrambing 6: yes (`1`) or no (`0`)
 `wordsf`           |   Sum of financial words in word scramblings 1, 3, 4, and 6
 `lies`             |   Number of dishonest reports in decisions 1 through 5
 `beliefs`          |   Expected number of dishonest reports in decisions 1 through 5
 `prof`             |   Subject group: `0` (STUD), `1` (PROF), or `2` (STUDPROF)
 `norms_true1`      |   Social appropriateness assessment of an honest report in decision 1
 `norms_false1`     |   Social appropriateness assessment of a dishonest report in decision 1
 `norms_true2`      |   Social appropriateness assessment of an honest report in decision 2
 `norms_false2`     |   Social appropriateness assessment of a dishonest report in decision 2
 `norms_true3`      |   Social appropriateness assessment of an honest report in decision 3
 `norms_false3`     |   Social appropriateness assessment of a dishonest report in decision 3
 `norms_true4`      |   Social appropriateness assessment of an honest report in decision 4
 `norms_false5`     |   Social appropriateness assessment of a dishonest report in decision 4
 `norms_true5`      |   Social appropriateness assessment of an honest report in decision 5
 `norms_false5`     |   Social appropriateness assessment of a dishonest report in decision 5
 `norms_true`       |   Average social appropriateness assessment of an honest report
 `norms_false`      |   Average social appropriateness assessment of a dishonest report
 
 
 